---
title: "R Markdown Presentation & Plotly"
author: "Thawatchai Phakwithoonchai"
date: "3/6/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE, tidy=TRUE, tidy.opts=list(blank = FALSE, width.cutoff = 60)}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction  

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

\newpage

# Review criteria

The rubric contains the following two questions:  

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?  
2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?  

\newpage

# Getting the data

```{r Getting the data}
library(plotly)
data("diamonds")
summary(diamonds)
set.seed(1234)
data <- diamonds[sample(nrow(diamonds), 500), ] # Select the 500 samples
```

\newpage  

# Exploratory data analysis

```{r Exploratory data analysis, fig.align='center', tidy=TRUE}
plot <- plot_ly(data = data, x = ~table, y = ~depth, z = ~carat, type = "scatter3d", color = ~price, colors = "Spectral", size = 1, alpha = 0.8, mode = "markers")
plot
```

3d scatter plot was shown the relationship of 500 sample diamonds in corresponding to the following parameters:

1. dimension or size of diamonds (table and depth)  
2. price of diamonds (price)
2. quality of cut (color of plot: IF is best, while I1 is worst)
3. weight of diamonds i.e. carat (size of scatter points)

# Thanks !!!
